%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same
% directory as this .tex file. These files provide the resume style and themes
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{David} % Your first name
\familyname{Tran} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Research Statement}
% \address{W. Ethan Eagle}{}
% \mobile{(302) 584 3464}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
\email{dtran253@uwo.ca}
% \homepage{staff.org.edu/~jsmith}{staff.org.edu/$\sim$jsmith} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\extrainfo{additional information}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}
\makecvtitle % Print the CV title
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Background and Experience}
I am entering the final year of my Bachelor's with a dual in Honors Computer Science and a Major in Mathematics and currently hold the highest standing in the Department of Computer Science. I have experience in machine learning and computational neuroscience research: I was an undergraduate researcher at Western's Brain and Mind Institute under the supervision of Dr. Jörn Diedrichsen with funding from NSERC's USRA. We developed a novel architecture for generating functional parcellations of the cerebellum using fMRI data, which involved conducting research in problems related to Bayesian unsupervised learning, approximate infererence, and hidden Markov models.
\\\\
Apart from research, I also have professional experience in software engineering. Most recently, I was a software engineer in Silicon Valley at Snowflake, a software company specializing in high-performing and highly-scalable distributed computing. Even as an engineer, my interests lean toward research work: at Snowflake the body of my work was mainly exploratory and experimental, involving the discovery of optimizations for the perfomance of the execution platform.

%----------------------------------------------------------------------------------------
\section{Current Research Interests}
This year, I enrolled in a graduate reading course on spectral geometry taught by Dr. Masoud Khalkhali, which was unfortunately disbanded due to lack of student interest. In spite of this, I have been studying Riemannian manifolds and spectral geometry in a self-directed manner out of interest. As a bonus, I am interested to see if there are connections between the tools used in spectral geometry to study the geometry of manifolds that can be applied to the problems in information geometry found in theoretical machine learning (for example, in relation to the manifold hypothesis).
\\\\
Additionally, I have been attending the series of talks in quantum computing and quantum information theory throughout the year organized by Dr. Ashgar Ghorbanpour. As a result, my undergraduate thesis in progress, supervised by Dr. Khalkhali, is in the field of quantum information theory, specifically in quantum error-correcting codes. I would like to continue this research throughout the summer.

\end{document}